---
title: "Checks Planejamento"
output: 
  rmdformats::robobook:
    toc: 3
    toc_float: true
date: "`r format(Sys.time())`"
---

```{r setup, include=FALSE}
library(checksplanejamento)

knitr::opts_chunk$set(rownames.print = FALSE)

old_hook <- knitr::knit_hooks$get("document")
knitr::knit_hooks$set(document = checksplanejamento::document_hook,
                      check = checksplanejamento::check_hook)

CHECK_COUNT <- list(pass = 0, fail = 0)

sigplan <- read_datapackage("datapackages/sigplan/datapackage.json")
sisor <- read_datapackage("datapackages/sisor/datapackage.json")
aux <- read_datapackage("datapackages/auxiliares/datapackage.json")
```

## check_area_tematica_exists

### [check_area_tematica_exists_programas](https://splor-mg.github.io/checks-planejamento/reference/check_area_tematica_exists_programas.html)

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_programas(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

### [check_area_tematica_exists_acoes](https://splor-mg.github.io/checks-planejamento/reference/check_area_tematica_exists_acoes.html)

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_acoes(sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### [check_area_tematica_exists_localizadores](https://splor-mg.github.io/checks-planejamento/reference/check_area_tematica_exists_localizadores.html)

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_localizadores(sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

## check_count

### [check_count_programas](https://splor-mg.github.io/checks-planejamento/reference/check_count_programas.html)

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas(sigplan$programas_planejamento, sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### [check_count_programas_is_deleted](https://splor-mg.github.io/checks-planejamento/reference/check_count_programas_is_deleted.html)

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas_is_deleted(sigplan$programas_planejamento, sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### [check_count_programas_is_new](https://splor-mg.github.io/checks-planejamento/reference/check_count_programas_is_new.html)

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas_is_new(sigplan$programas_planejamento, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### [check_count_acoes](https://splor-mg.github.io/checks-planejamento/reference/check_count_acoes.html)

```{r, check=TRUE, echo=FALSE}
check <- check_count_acoes(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### [check_count_acoes_is_deleted](https://splor-mg.github.io/checks-planejamento/reference/check_count_acoes_is_deleted.html)

```{r, check=TRUE, echo=FALSE}
check <- check_count_acoes_is_deleted(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

## check_detalhamento_obras

### [check_detalhamento_obras_orcam_fiscal_tesouro](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_fiscal_tesouro.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_tesouro(sisor$base_qdd_fiscal, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### [check_detalhamento_obras_orcam_fiscal_tesouro_plurianual](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_fiscal_tesouro_plurianual.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_tesouro_plurianual(sisor$base_qdd_plurianual, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### [check_detalhamento_obras_orcam_fiscal_outros](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_fiscal_outros.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_outros(sisor$base_qdd_fiscal, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### [check_detalhamento_obras_orcam_fiscal_outros_plurianual](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_fiscal_outros_plurianual.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_outros_plurianual(sisor$base_qdd_plurianual, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### [check_detalhamento_obras_orcam_investimento](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_investimento.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_investimento(sisor$base_qdd_investimento, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### [check_detalhamento_obras_orcam_investimento_plurianual](https://splor-mg.github.io/checks-planejamento/reference/check_detalhamento_obras_orcam_investimento_plurianual.html)

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_investimento_plurianual(sisor$base_qdd_plurianual_invest, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

## check_fechamento_fonte

### [check_fechamento_fonte_orcam_fiscal](https://splor-mg.github.io/checks-planejamento/reference/check_fechamento_fonte_orcam_fiscal.html)

```{r, check=TRUE, echo=FALSE}
check <- check_fechamento_fonte_orcam_fiscal(sisor$base_orcam_receita_fiscal, sisor$base_qdd_fiscal, output = TRUE)
render_table(check$info)
```

### [check_fechamento_fonte_orcam_investimento](https://splor-mg.github.io/checks-planejamento/reference/check_fechamento_fonte_orcam_investimento.html)

```{r, check=TRUE, echo=FALSE}
check <- check_fechamento_fonte_orcam_investimento(sisor$base_orcam_receita_investimento, sisor$base_qdd_investimento, output = TRUE)
render_table(check$info)
```

## check_indicadores

### [check_indicadores_consistency_indice_de_referencia_exists](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_consistency_indice_de_referencia_exists.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_consistency_indice_de_referencia_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_consistency_indice_de_referencia_missing](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_consistency_indice_de_referencia_missing.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_consistency_indice_de_referencia_missing(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_justificativa_indice_referencia_em_apuracao](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_justificativa_indice_referencia_em_apuracao.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_justificativa_indice_referencia_em_apuracao(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_indice_referencia_data_futura](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_indice_referencia_data_futura.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_data_futura(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_indice_referencia_exists](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_indice_referencia_exists.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_indice_referencia_zerado](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_indice_referencia_zerado.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_zerado(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_justificativa_previsao_em_apuracao](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_justificativa_previsao_em_apuracao.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_justificativa_previsao_em_apuracao(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### [check_indicadores_previsoes_exists](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_previsoes_exists.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_previsoes_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```


### [check_indicadores_previsoes_zeradas](https://splor-mg.github.io/checks-planejamento/reference/check_indicadores_previsoes_zeradas.html)

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_previsoes_zeradas(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

## check_intra_orcamentaria

### [check_intra_despesa](https://splor-mg.github.io/checks-planejamento/reference/check_intra_despesa.html)

```{r, check=TRUE, echo=FALSE}
check <- check_intra_despesa(sisor$base_orcam_despesa_item_fiscal, sisor$base_intra_orcamentaria_repasse, output = TRUE)
render_table(check$info)
```

### [check_intra_receita](https://splor-mg.github.io/checks-planejamento/reference/check_intra_receita.html)

```{r, check=TRUE, echo=FALSE}
check <- check_intra_receita(sisor$base_orcam_receita_fiscal, sisor$base_intra_orcamentaria_repasse, output = TRUE)
render_table(check$info)
```

### [check_intra_detalhamento](https://splor-mg.github.io/checks-planejamento/reference/check_intra_detalhamento.html)

```{r, check=TRUE, echo=FALSE}
check <- check_intra_detalhamento(sisor$base_intra_orcamentaria_detalhamento, output = TRUE)
render_table(check$info)
```

## check_limite

### [check_limite_ano0](https://splor-mg.github.io/checks-planejamento/reference/check_limite_ano0.html)

```{r, check=TRUE, echo=FALSE}
check <- check_limite_ano0(sisor$base_limite_cota, output = TRUE)
render_table(check$info)
```

### [check_limite_plurianual](https://splor-mg.github.io/checks-planejamento/reference/check_limite_plurianual.html)

```{r, check=TRUE, echo=FALSE}
check <- check_limite_plurianual(sisor$base_limite_cota, output = TRUE)
render_table(check$info)
```

## check_ods

### [check_ods_exists](https://splor-mg.github.io/checks-planejamento/reference/check_ods_exists.html)

```{r, check=TRUE, echo=FALSE}
check <- check_ods_exists(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

### [check_ods_consistency](https://splor-mg.github.io/checks-planejamento/reference/check_ods_consistency.html)

```{r, check=TRUE, echo=FALSE}
check <- check_ods_consistency(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

## [check_projetos_estrategicos](https://splor-mg.github.io/checks-planejamento/reference/check_projetos_estrategicos.html)

```{r, check=TRUE, echo=FALSE}
check <- check_projetos_estrategicos(sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

## [check_repasse_recursos](https://splor-mg.github.io/checks-planejamento/reference/check_repasse_recursos.html)

```{r, check=TRUE, echo=FALSE}
check <- check_repasse_recursos(sisor$base_qdd_fiscal, sisor$base_repasse_recursos, output = TRUE)
render_table(check$info)
```

## [check_setor_governo](https://splor-mg.github.io/checks-planejamento/reference/check_setor_governo.html)

```{r, check=TRUE, echo=FALSE}
check <- check_setor_governo(sigplan$acoes_planejamento, aux$desc_setor_governo, output = TRUE)
render_table(check$info)
```

## check_valores_sigplan

### [check_valores_sigplan_localizadores](https://splor-mg.github.io/checks-planejamento/reference/check_valores_sigplan_localizadores.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sigplan_localizadores(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### [check_valores_sigplan_programas](https://splor-mg.github.io/checks-planejamento/reference/check_valores_sigplan_programas.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sigplan_programas(sigplan$acoes_planejamento, sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

## check_valores_sigplan_sisor

### [check_valores_qdd_fiscal](https://splor-mg.github.io/checks-planejamento/reference/check_valores_qdd_fiscal.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_fiscal(sisor$base_qdd_fiscal, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### [check_valores_qdd_plurianual](https://splor-mg.github.io/checks-planejamento/reference/check_valores_qdd_plurianual.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_plurianual(sisor$base_qdd_plurianual, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### [check_valores_qdd_investimento](https://splor-mg.github.io/checks-planejamento/reference/check_valores_qdd_investimento.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_investimento(sisor$base_qdd_investimento, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### [check_valores_qdd_plurianual_invest](https://splor-mg.github.io/checks-planejamento/reference/check_valores_qdd_plurianual_invest.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_plurianual_invest(sisor$base_qdd_plurianual_invest, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

## [check_valores_sisor](https://splor-mg.github.io/checks-planejamento/reference/check_valores_sisor.html)

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sisor(sisor$base_qdd_fiscal, sisor$base_orcam_despesa_item_fiscal, output = TRUE)
render_table(check$info)
```

## Diagnóstico

### Conjuntos de Dados

```{r, echo = FALSE}
sigplan_descriptor <- jsonlite::read_json("datapackages/sigplan/datapackage.json")
sisor_descriptor <- jsonlite::read_json("datapackages/sisor/datapackage.json")
aux_descriptor <- jsonlite::read_json("datapackages/auxiliares/datapackage.json")

packages <- list(sigplan = sigplan_descriptor, 
                 sisor = sisor_descriptor, 
                 auxiliares = aux_descriptor) 
listviewer::jsonedit(packages)
```


### Session Info

```{r, echo = FALSE}
sessioninfo::session_info()
```

</details>