---
title: "Checklist para conferência das bases SIGPLAN/SISOR"
output: 
  rmdformats::robobook:
    toc: 3
    toc_float: true
date: "`r format(Sys.time())`"
---

```{r setup, include=FALSE}
library(checks.planejamento)

knitr::opts_chunk$set(rownames.print = FALSE)

old_hook <- knitr::knit_hooks$get("document")
knitr::knit_hooks$set(document = checks.planejamento::document_hook,
                      check = checks.planejamento::check_hook)

CHECK_COUNT <- list(pass = 0, fail = 0)

sigplan <- read_datapackage("datapackages/sigplan/datapackage.json")
sisor <- read_datapackage("datapackages/sisor/datapackage.json")
aux <- read_datapackage("datapackages/auxiliares/datapackage.json")
```

## check_area_tematica_exists

### check_area_tematica_exists_programas

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_programas(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

### check_area_tematica_exists_acoes

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_acoes(sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### check_area_tematica_exists_localizadores

```{r, check=TRUE, echo=FALSE}
check <- check_area_tematica_exists_localizadores(sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

## check_count

### check_count_programas

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas(sigplan$programas_planejamento, sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### check_count_programas_is_deleted

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas_is_deleted(sigplan$programas_planejamento, sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### check_count_programas_is_new

```{r, check=TRUE, echo=FALSE}
check <- check_count_programas_is_new(sigplan$programas_planejamento, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### check_count_acoes

```{r, check=TRUE, echo=FALSE}
check <- check_count_acoes(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### check_count_acoes_is_deleted

```{r, check=TRUE, echo=FALSE}
check <- check_count_acoes_is_deleted(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

## check_detalhamento_obras

### check_detalhamento_obras_orcam_fiscal_tesouro

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_tesouro(sisor$base_qdd_fiscal, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### check_detalhamento_obras_orcam_fiscal_tesouro_plurianual

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_tesouro_plurianual(sisor$base_qdd_plurianual, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### check_detalhamento_obras_orcam_fiscal_outros

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_outros(sisor$base_qdd_fiscal, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### check_detalhamento_obras_orcam_fiscal_outros_plurianual

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_fiscal_outros_plurianual(sisor$base_qdd_plurianual, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### check_detalhamento_obras_orcam_investimento

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_investimento(sisor$base_qdd_investimento, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

### check_detalhamento_obras_orcam_investimento_plurianual

```{r, check=TRUE, echo=FALSE}
check <- check_detalhamento_obras_orcam_investimento_plurianual(sisor$base_qdd_plurianual_invest, sisor$base_detalhamento_obras, output = TRUE)
render_table(check$info)
```

## check_fechamento_fonte

### check_fechamento_fonte_orcam_fiscal

```{r, check=TRUE, echo=FALSE}
check <- check_fechamento_fonte_orcam_fiscal(sisor$base_orcam_receita_fiscal, sisor$base_qdd_fiscal, output = TRUE)
render_table(check$info)
```

### check_fechamento_fonte_orcam_investimento

```{r, check=TRUE, echo=FALSE}
check <- check_fechamento_fonte_orcam_investimento(sisor$base_orcam_receita_investimento, sisor$base_qdd_investimento, output = TRUE)
render_table(check$info)
```

## check_indicadores

### check_indicadores_consistency_indice_de_referencia_exists

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_consistency_indice_de_referencia_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_consistency_indice_de_referencia_missing

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_consistency_indice_de_referencia_missing(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_justificativa_indice_referencia_em_apuracao

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_justificativa_indice_referencia_em_apuracao(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_indice_referencia_data_futura

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_data_futura(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_indice_referencia_exists

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_indice_referencia_zerado

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_indice_referencia_zerado(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_justificativa_previsao_em_apuracao

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_justificativa_previsao_em_apuracao(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

### check_indicadores_previsoes_exists

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_previsoes_exists(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```


### check_indicadores_previsoes_zeradas

```{r, check=TRUE, echo=FALSE}
check <- check_indicadores_previsoes_zeradas(sigplan$indicadores_planejamento, output = TRUE)
render_table(check$info)
```

## check_intra_orcamentaria

### check_intra_despesa

```{r, check=TRUE, echo=FALSE}
check <- check_intra_despesa(sisor$base_orcam_despesa_item_fiscal, sisor$base_intra_orcamentaria_repasse, output = TRUE)
render_table(check$info)
```

### check_intra_receita

```{r, check=TRUE, echo=FALSE}
check <- check_intra_receita(sisor$base_orcam_receita_fiscal, sisor$base_intra_orcamentaria_repasse, output = TRUE)
render_table(check$info)
```

### check_intra_detalhamento

```{r, check=TRUE, echo=FALSE}
check <- check_intra_detalhamento(sisor$base_intra_orcamentaria_detalhamento, output = TRUE)
render_table(check$info)
```

## check_limite

### check_limite_ano0

```{r, check=TRUE, echo=FALSE}
check <- check_limite_ano0(sisor$base_limite_cota, output = TRUE)
render_table(check$info)
```

### check_limite_plurianual

```{r, check=TRUE, echo=FALSE}
check <- check_limite_plurianual(sisor$base_limite_cota, output = TRUE)
render_table(check$info)
```

## check_ods

### check_ods_exists

```{r, check=TRUE, echo=FALSE}
check <- check_ods_exists(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

### check_ods_consistency

```{r, check=TRUE, echo=FALSE}
check <- check_ods_consistency(sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

## check_projetos_estrategicos

```{r, check=TRUE, echo=FALSE}
check <- check_projetos_estrategicos(sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

## check_repasse_recursos

```{r, check=TRUE, echo=FALSE}
check <- check_repasse_recursos(sisor$base_qdd_fiscal, sisor$base_repasse_recursos, output = TRUE)
render_table(check$info)
```

## check_setor_governo

```{r, check=TRUE, echo=FALSE}
check <- check_setor_governo(sigplan$acoes_planejamento, aux$desc_setor_governo, output = TRUE)
render_table(check$info)
```

## check_valores_sigplan

### check_valores_sigplan_localizadores

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sigplan_localizadores(sigplan$acoes_planejamento, sigplan$localizadores_todos_planejamento, output = TRUE)
render_table(check$info)
```

### check_valores_sigplan_programas

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sigplan_programas(sigplan$acoes_planejamento, sigplan$programas_planejamento, output = TRUE)
render_table(check$info)
```

## check_valores_sigplan_sisor

### check_valores_qdd_fiscal

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_fiscal(sisor$base_qdd_fiscal, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### check_valores_qdd_plurianual

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_plurianual(sisor$base_qdd_plurianual, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### check_valores_qdd_investimento

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_investimento(sisor$base_qdd_investimento, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

### check_valores_qdd_plurianual_invest

```{r, check=TRUE, echo=FALSE}
check <- check_valores_qdd_plurianual_invest(sisor$base_qdd_plurianual_invest, sigplan$acoes_planejamento, output = TRUE)
render_table(check$info)
```

## check_valores_sisor

```{r, check=TRUE, echo=FALSE}
check <- check_valores_sisor(sisor$base_qdd_fiscal, sisor$base_orcam_despesa_item_fiscal, output = TRUE)
render_table(check$info)
```
